Case for Support

### 2021-11-16 application/caseForSupport.tex
Moved files to application dir
Updates from Overleaf

\documentclass[a4paper,11point]{article}
\usepackage[margin=2cm]{geometry}

@@

\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}%
            {-2.5ex\@plus -1ex \@minus -.25ex}%
            {1.25ex \@plus .25ex}%
            {\normalfont\normalsize\bfseries}}
\makeatother
\setcounter{secnumdepth}{4} % how many sectioning levels to assign numbers to
\setcounter{tocdepth}{4}    % how many sectioning levels to show in ToC

@@

\section{Background to the resource}

@@

@@

\section{Potential for economic and societal impact}

@@

\bibliographystyle{apalike}
\bibliography{bonsai,epsrcSoftwareForResearchCommunities,monitoringBehavior,stateSpaceModels,machineLearning,gaussianProcesses}

>>>>

\documentclass[a4paper,11point]{article}
\usepackage[margin=2cm]{geometry}
%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
% \usepackage{microtype}      % fine pdf font control

\usepackage[scaled=0.92]{helvet} \renewcommand{\familydefault}{\sfdefault}
\usepackage{xcolor} % -- loaded by tikz

@@

\usepackage{wrapfig}

\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}%
            {-2.5ex\@plus -1ex \@minus -.25ex}%
            {1.25ex \@plus .25ex}%
            {\normalfont\normalsize\bfseries}}
\makeatother
\setcounter{secnumdepth}{4} % how many sectioning levels to assign numbers to
\setcounter{tocdepth}{4}    % how many sectioning levels to show in ToC
\usepackage[small]{titlesec} % format section titles

@@

@@

\input resourceManagement

@@

\section{Potential for economic and societal impact}
\textbf{Understanding the brain.} Systems neuroscientists aim to uncover how adaptive behaviour arises
from computation in neural circuits in different brain regions. Extending the Bonsai ecosystem will facilitate experiments that connect neural circuits with elemental behavioural processes. Long-term, this research will help identify the missing links between circuit dysfunction and behavioural deficits in neurological or mental health disorders, and will pave the way for the development of new neural circuit biomarkers and therapies. The Bonsai ecosystem will also enable the experimental testing of emerging theories of brain function and learning, and thus contribute to the neuro-inspired machine learning algorithms that fuel intelligent technologies, increasingly important in our society.

\textbf{Improve reproducibility in behavioural and brain sciences.} Lack of reproducible results slows down scientific progress and incurs personal and economic costs to scientists and funders.  In neuroscience,  many behavioural and neural animal studies have been to be difficult to reproduce, and experiments are rarely replicated across laboratories. By creating a resource that standardises and enables reproducible experimental design/control, as well as analysis of neural and behavioural data, the Bonsai ecosystem will allow multiple laboratories to implement and align experimental and analytical protocols as closely as possible.

\textbf{Improve efficiency of research.} Most neuroscience laboratories worldwide develop custom, unique solutions to their experimental control and analysis needs. Some laboratories also lack the technical know-how to either develop their own software for experimental hardware control or write software for the state-of-the-art analysis of rich neural and behavioural data, increasingly reliant on latest machine learning algorithms. The proposed upgrading of the open-source and community empowered Bonsai ecosystem with a toolbox of online and offline analytical tools, that can dovetail with closed-loop experimental requirements, will (i) allow the deployment of such tools into laboratories that lack the expertise, (ii) reduce the need to reinvent the same tools in multiple labs (cost/time efficiency) and (iii) concomitantly streamline and standardise the experimental data processing streams in systems neuroscience.

@@

\bibliographystyle{apalike}
\bibliography{bonsai,epsrcSoftwareForResearchCommunities,monitoringBehavior,stateSpaceModels,machineLearning,gaussianProcesses,spikeSorting}
